Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-06 paper/paper-nature_format.tex
updated paper version

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 5, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many Commonwealth countries such as Canada,
the United Kingdom, and Australia (Vice and Farrell 2017). Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
al. 2017). Having a digitized version of Hansard enables researchers to
conduct text analysis and statistical modelling. Following the lead of
that project, in this paper we introduce a similar database for
Australia. This is composed of individual datasets for each sitting day
in the House of Representatives from 1998 to 2022, containing details on
everything said in parliament in a form that can be readily used by
researchers. With the development of tools for large-scale text
analysis, this database will serve as a resource for understanding
political behaviour in Australia over time.

The Australian House of Representatives performs a number of crucial
governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1). The House
operates under a parallel chamber setup, meaning there are two debate
venues where proceedings take place: the Chamber, and the Federation
Chamber. Sittings of the House follow a predefined order of business,
regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of these proceedings on which Hansard is based, and it is
essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance, Sherratt (2016) created an online, easy to read
database of Hansard from 1901 to 1980 using the XML files. These data
can be navigated by year, parliament, people, and bills (Sherratt 2016).
To make the Australian Parliamentary Handbook more accessible, Leslie
(2021) has released an \texttt{R} package which includes data on all
Members of the Australian House of Representatives from 1945 to 2019.
Further, Alexander and Hodgetts (2021) created the
\texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used online
Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where the Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. Fraussen,
Graham, and Halpin (2018) use Hansard to quantify political prominence
by investigating strategic mentions of interest groups by elected
officials. Finally, Alexander and Alexander (2021) construct a dataset
of the Australian Hansard, along with an analysis of the effect of
elections and changes in Prime Ministers upon topics mentioned in
parliament. Alexander and Alexander (2021) created this database with
the static PDF versions of Hansard, using OCR to digitize these files
into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

Our database contains one comma-separated value (CSV) and one parquet
file for each sitting day of the House of Representatives from 02 March
1998 to 08 September 2022. We developed four scripts to produce these
files. Each script parses Hansard documents from a specific portion of
the 1998 to 2022 time frame.

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Finally, we discuss the script we developed to fill in remaining missing
details on the member of parliament speaking, which each file in our
database was passed to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the member of parliament whose turn it is to speak and
the time of their first statement. Unsurprisingly, speeches rarely go
uninterrupted in parliamentary debate settings --- they are often
composed of a series of interjections and continuations. These
statements are categorized under different sub-nodes depending on their
nature, such as \texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by Wickham (2014). These contain all
parsed text elements, where each statement is separated onto its own row
with details about the member of parliament who is speaking, and rows
are maintained in chronological order. This first involved correcting
the variable classes and adding several indicator variables to
differentiate where statements came from, such as Chamber versus
Federation Chamber or \texttt{\textless{}subdebate.1\textgreater{}}
versus \texttt{\textless{}subdebate.2\textgreater{}}. The next key task
stemmed from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted. These became apparent as we ran
our script on XML files from earlier sitting days. Some changes are as
subtle as a differently named child-node, while others are as extensive
as a completely different nesting structure. Smaller changes were
accounted for as we became aware of them, and embedded into the code in
a way that would not cause issues for parsing more current Hansards with
subtle differences in formatting. However, as mentioned, more
significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards.
Further not every sitting day contains every possible XML element. For
example, some days did not have
\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse exists in the file.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in mid-2012
(House of Representatives 2018, ch.~21). As a result, the child-node
under which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments, and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement, such as their party and
electorate.

In contrast, the speech contents in XMLs from 1998 up to and including
24 March 2011 are nested differently --- there is no
\texttt{\textless{}talk.text\textgreater{}} node. Rather than this
single child-node that contains all speech content, statements are
categorized in individual child-nodes. This means that unlike our code
for parsing more current Hansards, we cannot specify a single XPath
expression such as
``\texttt{chamber.xscript//debate//speech/talk.text}'' to extract all
speeches, in their entirety, at once. This difference in nesting
structure made many components of our second script unusable for
processing transcripts preceding 10 May 2011, and required us to change
our data processing approach considerably.

Since the earlier Hansard XMLs do not have a
\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
straightforward way to preserve the ordering of statements and to parse
all speech contents at once was to parse from the
\texttt{\textless{}debate\textgreater{}} element directly. The reason we
did not use its \texttt{\textless{}speech\textgreater{}} child-node is
because every speech has a unique structure of node children, and this
makes it difficult to write code for data cleaning which is
generalizable across all speeches and sitting days. The challenge with
parsing through the \texttt{\textless{}debate\textgreater{}} element is
that every piece of data stored in that element is parsed as a single
string, including all \texttt{\textless{}talk.start\textgreater{}} data,
and all nested sub-debate data. For example, the data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
members of the House can ask ministers two types of questions: questions
in writing which are written in advance, or questions without notice
which are asked verbally in the Chamber and are responded to in real
time (House of Representatives 2021). Questions without notice are
included directly in the \texttt{"chamber.xscript"} child node, with
sub-child nodes called \texttt{"question"} and \texttt{"answer"} to
differentiate the two. Questions in writing, however, are embedded in
their own child node called \texttt{"answers.to.questions"} at the end
of the XML file.

@@

As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
XMLs contain a series of child-nodes which exist to capture the
structure of interruptions in that speech. Figure~\ref{fig-xml3}
provides an example of this, where the speech was interrupted by a
comment from the Deputy Speaker, and then the member continued their
speech. Looking at the element names highlighted in blue, these
child-nodes do not contain the actual text for the interjection or
continuation --- this text is embedded within the speech above it.
However, as shown by the content highlighted in pink in
Figure~\ref{fig-xml3}, we were able to extract useful details on the
individual interjecting which we could use later. Making use of this
structure, we extracted names and information of all individuals that
were categorized within the XML as interjections. We stored this as a
dataframe called \texttt{"interject"}. We decided not to include this
data in our final database, as it is embedded in our resulting datasets
which have a flag for interjections.

@@

We then created lists using both the \texttt{interject} and
\texttt{main} dataframes to capture all the names of individuals who
spoke that day. We added the names of all members in a number of unique
formats, due to the frequent variation in how names are transcribed in
Hansard. When a member interjects or continues a speech, the usual form
of their name is a title followed by their first name or first initial
and/or last name. There is also variation in the capitalization of these
names.\footnote{Sometimes when someone's first name is included, only
  their last name is capitalized, while sometimes their full name is
  capitalized, or other times neither are capitalized.} Another source
of variation is in individuals with more than one first name, as
sometimes only their initial first name is written, while other times
their entire first name is written. Additionally, some surnames have
punctuation, and some surnames have specific capitalization such as
``McCormack'', where even in full capitalization, the first ``c''
remains lower case. This variation demands careful consideration when
writing regular expression patterns. In these lists we also accounted
for any general interjection statements that were not attributed to an
individual, such as ``An opposition member interjecting-''.

Having these lists enabled us to extract the names of members and their
associated titles as they exist in the text, by searching for exact
matches with regular expression patterns. We then used these extracted
names to split all the speeches, using regular expressions with
lookarounds. A lookaround can be added to a regular expression pattern
to enhance the specificity of matches. These were used to ensure that
the text was not being split in the wrong places, such as places where
members were being named in the statement of another member.

@@

\caption{\label{fig-lookup}First 10 rows of lookup table from 19 October
2017 Hansard processing}

@@

Next, we merged our main dataframe with the lookup table to replace any
incomplete names with their full names, and to fill in any gaps with
available name ID, electorate, party, gender, and unique ID information.
Finally, we were able to add a flag for interjections. Grouping our data
by the speech number, we defined an interjection as a statement made by
anyone who is not the Speaker, the Deputy Speaker, or the member whose
turn it was to speak. Figure~\ref{fig-interject} provides an example of
a Federation Chamber proceeding with interjections. Statements made by
the member whose turn it was to speak, or by the Deputy Speaker Maria
Vamvakinou, are not flagged as interjections.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
in Section~\ref{sec-diff}, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml3},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed.\footnote{While most statements
  were categorized in their own child-node and hence captured through
  pattern-based separation, some were not individually categorized, and
  had to be split manually in this step.}

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 6, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in many other Commonwealth countries, such as
Canada and Australia (Vice and Farrell 2017). Given the content and
magnitude of these records, they have significance, particularly in the
context of political science research. In the case of Canada, the
Hansard has been digitized for 1901 to 2019 (Beelen et al. 2017). Having
a digitized version of Hansard enables researchers to conduct text
analysis and statistical modelling. Following the lead of that project,
in this paper we introduce a similar database for Australia. This is
composed of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form that can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a resource for understanding political behaviour in
Australia over time.

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure (House of Representatives 2018, ch.~1).
Politicians in the House are referred to as Members of Parliament (MPs).
The House operates under a parallel chamber setup, meaning there are two
debate venues where proceedings take place: the Chamber, and the
Federation Chamber. Sittings of the House follow a predefined order of
business, regulated by procedural rules called standing orders (House of
Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
number of scheduled proceedings including debates on government
business, 90 second member statements, and Question Time (House of
Representatives 2018, ch.~8). The Federation Chamber was created in 1994
as a subordinate debate venue of the Chamber. This allows for better
time management of House business as its proceedings occur
simultaneously with those of the Chamber (House of Representatives 2018,
ch.~21). Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of these proceedings on which Hansard is based, and it is
essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases of
usable, complete data based on content from the Australian Parliament
website. For instance, Sherratt (2016) created an online, easy to read
database of Hansard from 1901 to 1980 using the XML files. These data
can be navigated by year, parliament, people, and bills (Sherratt 2016).
To make the Australian Parliamentary Handbook more accessible, Leslie
(2021) has released an \texttt{R} package which includes data on all MPs
from 1945 to 2019. Further, Alexander and Hodgetts (2021) created the
\texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, Salisbury (2011) used the Hansard
to investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark. Rasiah (2010) worked
with Question Time data from Hansard transcripts during February and
March of 2003, to investigate resistance of politicians in answering
questions about Iraq. Fraussen, Graham, and Halpin (2018) use Hansard to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials. Finally, Alexander and Alexander
(2021) construct a dataset of the Australian Hansard, along with an
analysis of the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament. Alexander and Alexander (2021) created
this database with the static PDF versions of Hansard, using OCR to
digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

@@

Our database contains one comma-separated value (CSV) file and one
parquet file for each sitting day of the House of Representatives from
02 March 1998 to 08 September 2022. We developed four scripts to produce
these files. Each script parses Hansard documents from a specific
portion of the 1998 to 2022 time frame.

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Finally, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child nodes,
where the first child node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the MP whose turn it is to speak and the time of their
first statement. Unsurprisingly, speeches rarely go uninterrupted in
parliamentary debate settings --- they are often composed of a series of
interjections and continuations. These statements are categorized under
different sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by Wickham (2014). These contain all
parsed text elements, where each statement is separated onto its own row
with details about the MP who is speaking, and rows are maintained in
chronological order. This first involved correcting the variable classes
and adding several indicator variables to differentiate where statements
came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

Since we are looking at a wide time span of documents, there are many
changes in the way they are formatted. These became apparent as we ran
our script on XML files from earlier sitting days. Some changes are as
subtle as a differently named child node, while others are as extensive
as a completely different nesting structure. Smaller changes were
accounted for as we became aware of them, and embedded into the code in
a way that would not cause issues for parsing more current Hansards with
subtle differences in formatting. However, as mentioned, more
significant changes in the XML structure of Hansard are what
necessitated the development of separate scripts as we worked backwards.
Further not every sitting day contains every possible XML element. For
example, some days did not have
\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
not have a Federation Chamber proceeding. To improve the
generalizability of these scripts, if-else statements were embedded
within the code wherever an error might arise due to a missing element.
For example, the entire Federation Chamber block of code is wrapped in
an if-else statement for each script, so that it only executes if what
the code attempts to parse exists in the file.

@@

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in mid-2012
(House of Representatives 2018, ch.~21). As a result, the child node
under which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments, and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by an MP, and then
continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the MP who made each statement, such as their party and
electorate.

In contrast, the speech contents in XMLs from 1998 up to and including
24 March 2011 are nested differently --- there is no
\texttt{\textless{}talk.text\textgreater{}} node. Rather than this
single child node that contains all speech content, statements are
categorized in individual child nodes. This means that unlike our code
for parsing more current Hansards, we cannot specify a single XPath
expression such as
``\texttt{chamber.xscript//debate//speech/talk.text}'' to extract all
speeches, in their entirety, at once. This difference in nesting
structure made many components of our second script unusable for
processing transcripts preceding 10 May 2011, and required us to change
our data processing approach considerably.

Since the earlier Hansard XMLs do not have a
\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
straightforward way to preserve the ordering of statements and to parse
all speech contents at once was to parse from the
\texttt{\textless{}debate\textgreater{}} element directly. The reason we
did not use its \texttt{\textless{}speech\textgreater{}} child node is
because every speech has a unique structure of node children, and this
makes it difficult to write code for data cleaning which is
generalizable across all speeches and sitting days. The challenge with
parsing through the \texttt{\textless{}debate\textgreater{}} element is
that every piece of data stored in that element is parsed as a single
string, including all \texttt{\textless{}talk.start\textgreater{}} data,
and all nested sub-debate data. For example, the data shown in
Figure~\ref{fig-patternEX} would be parsed as a single string preceding
the speech content, like so:

@@

A key characteristic of the Australian parliamentary system is the
ability for the executive government to be held accountable for their
decisions. One core mechanism by which this is achieved is called
Question Time. This is a period of each sitting day in the Chamber where
MPs can ask ministers two types of questions: questions in writing which
are written in advance, or questions without notice which are asked
verbally in the Chamber and are responded to in real time (House of
Representatives 2021). Questions without notice are included directly in
the \texttt{"chamber.xscript"} child node, with sub-child nodes called
\texttt{"question"} and \texttt{"answer"} to differentiate the two.
Questions in writing, however, are embedded in their own child node
called \texttt{"answers.to.questions"} at the end of the XML file.

@@

As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
XMLs contain a series of child nodes which exist to capture the
structure of interruptions in that speech. Figure~\ref{fig-xml3}
provides an example of this, where the speech was interrupted by a
comment from the Deputy Speaker, and then the MP continued their speech.
Looking at the element names highlighted in blue, these child nodes do
not contain the actual text for the interjection or continuation ---
this text is embedded within the speech above it. However, as shown by
the content highlighted in pink in Figure~\ref{fig-xml3}, we were able
to extract useful details on the individual interjecting which we could
use later. Making use of this structure, we extracted names and
information of all individuals that were categorized within the XML as
interjections. We stored this as a dataframe called
\texttt{"interject"}. We decided not to include this data in our final
database, as it is embedded in our resulting datasets which have a flag
for interjections.

@@

We then created lists using both the \texttt{interject} and
\texttt{main} dataframes to capture all the names of individuals who
spoke that day. We added the names of all MPs in a number of unique
formats, due to the frequent variation in how names are transcribed in
Hansard. When an MP interjects or continues a speech, the usual form of
their name is a title followed by their first name or first initial
and/or last name. There is also variation in the capitalization of these
names.\footnote{Sometimes when someone's first name is included, only
  their last name is capitalized, while sometimes their full name is
  capitalized, or other times neither are capitalized.} Another source
of variation is in individuals with more than one first name, as
sometimes only their initial first name is written, while other times
their entire first name is written. Additionally, some surnames have
punctuation, and some surnames have specific capitalization such as
``McCormack'', where even in full capitalization, the first ``c''
remains lower case. This variation demands careful consideration when
writing regular expression patterns. In these lists we also accounted
for any general interjection statements that were not attributed to an
individual, such as ``An opposition member interjecting-''.

Having these lists enabled us to extract the names of MPs and their
associated titles as they exist in the text, by searching for exact
matches with regular expression patterns. We then used these extracted
names to split all the speeches, using regular expressions with
lookarounds. A lookaround can be added to a regular expression pattern
to enhance the specificity of matches. These were used to ensure that
the text was not being split in the wrong places, such as places where
MPs were being named in the statement of another MP.

@@

\caption{\label{fig-lookup}First 10 rows of the lookup table from 19
October 2017 Hansard processing}

@@

Next, we merged our main dataframe with the lookup table to replace any
incomplete names with their full names, and to fill in any gaps with
available name ID, electorate, party, gender, and unique ID information.
Finally, we were able to add a flag for interjections. Grouping our data
by the speech number, we defined an interjection as a statement made by
anyone who is not the Speaker, the Deputy Speaker, or the MP whose turn
it was to speak. Figure~\ref{fig-interject} provides an example of a
Federation Chamber proceeding with interjections. Statements made by the
MP whose turn it was to speak, or by the Deputy Speaker Maria
Vamvakinou, are not flagged as interjections.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
in Section~\ref{sec-diff}, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml3},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed.\footnote{While most statements
  were categorized in their own child node and hence captured through
  pattern-based separation, some were not individually categorized, and
  had to be split manually in this step.}
